Supporting Information

### 2018-03-30 SupportingInformation.Rmd
added back in a newpage command to get it to knit

---
title: "Supporting Information"
author: "Shyamolina Ghosh and Daniel Reuman"
date: "February 12, 2018"
geometry: "left=1cm,right=1cm,top=2.5cm,bottom=2.8cm"

@@

## Results: abundance data for *Ceratium furca* in UK seas \label{Ex_pns}

>>>>

---
title: "Supporting Information"
author: "S. Ghosh, T. Loecke, C.P. Reid, Daniel Reuman"
date: "February 12, 2018"
geometry: "left=1cm,right=1cm,top=2.5cm,bottom=2.8cm"

@@

\newpage
## Results: abundance data for *Ceratium furca* in UK seas \label{Ex_pns}
